$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Removed an unused definition in the appendix on RGE contributions
Added start of gauge coupling beta functions to appendix

$m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$. The
one- and two-loop contributions to the $\beta$ function for $\lambda$

@@

Additionally, in order to keep our expressions compact we also use the notation
\Sigma_{\tilde{Q}}=\sum_i \tilde{Q}_i^2, \qquad \Pi_{\tilde{Q}}=\sum_i \tilde{Q}_i^4
to denote sums over the $U(1)'$ charges, and
Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised.

>>>>

$m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$. Neglecting kinetic
mixing, the two-loop $\beta$ functions for the gauge couplings read
\begin{subequations}\label{eq:USSMGaugeBetas}
\beta_{g_1}^{(1)}&=\frac{48}{5}g_1^3,\label{eq:USSMg1BetaOneLoop}\\
\beta_{g_1}^{(2)}&=\frac{2}{25},\label{eq:USSMg1BetaTwoLoop}\\
\beta_{g_2}^{(1)}&=4g_2^3,\label{eq:USSMg2BetaOneLoop}\\
\beta_{g_3}^{(1)}&=0,\label{eq:USSMg3BetaOneLoop}\\
\beta_{g_1'}^{(1)}&=g_1'^3\Sigma_{\tilde{Q}},\label{eq:USSMg1pBetaOneLoop}
In order to keep our expressions compact we have used the notation
\Sigma_{\tilde{Q}}=\sum_i \tilde{Q}_i^2
to denote the trace over the $U(1)'$ charges, and
Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised.\\ \\
The one- and two-loop contributions to the $\beta$ function for $\lambda$

@@
